<span style='line-height:60px; font-size:60px'>Changing communicative needs <br>and the structure of the lexicon:<br>corpus-based and experimental approaches</span></font>

### 2020-04-02 cletalk2020/index.Rmd
update

---
title: "<span style='line-height:60px; font-size:60px'>Changing communicative needs <br>and the structure of the lexicon:<br>corpus-based and experimental approaches</span></font>"
author: "<font size=6>Andres Karjus<br></font><font size=5>PhD student, Centre for Language Evolution, University of Edinburgh<br>Supervised by Kenny Smith, Richard A. Blythe, Simon Kirby</font>"
date: "<font size=5>CLE research group talk, 31.03.2020 &#8226; Slides online: andreskarjus.github.io/cletalk2020</font>"
output:
  xaringan::moon_reader:
    css: img/xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: false
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
---
class: inverse
# Communicative need and language change

>>>>

---
title: "<span style='line-height:60px; font-size:60px'>Changing communicative needs <br>and the structure of the lexicon:<br>corpus-based and experimental approaches</span></font>"
author: "<font size=6>Andres Karjus<br></font><font size=5>PhD student, Centre for Language Evolution, University of Edinburgh<br>Supervised by Kenny Smith, Richard A. Blythe, Simon Kirby</font>"
date: "<font size=5>CLE talk, 31.03.2020 &#8226; Slides: andreskarjus.github.io/cletalk2020 &#8226; Twitter: @andreskarjus</font>"
output:
  xaringan::moon_reader:
    css: img/xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: false
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
---
class: inverse
# Communicative need and language change
